Supplementary appendix

### 2019-04-13 paper2_APPENDIX_rev_01.Rmd
Add files via upload

```{r , include=FALSE, echo=FALSE}
source("SVIVA_exp2_dm_03.R")

SVIVA1_01 = read.csv("SVIVA1_01.csv")
CELEBS_00 = read.csv("CELEBS.csv")
```

```{r , include=FALSE, echo=FALSE}
library(tidyverse)
library(sjPlot)
library(stargazer)
```

@@

```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
knitr::include_graphics("D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_air_model.jpg")
```

@@

```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
knitr::include_graphics("D:/UNIVERSITY/R/SVIVA/experiment 2 01-2018/myfigures/fake_waste_model.jpg")
```

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
set_theme("scatterw")

sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_recognize,
        geom.size = 0.9,
        ylim=c(0,155),
        axis.title="",
        title = "Real logo")

sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_recognize,
        geom.size = 0.9,
        ylim=c(0,155),
        axis.title="",
        title = "Fake logo")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
set_theme("scatterw")

sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,160),
        axis.title="",
        title = "Real logo")

sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,160),
        axis.title="",
       title = "Fake logo")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real celeb (Tal Friedman)")

sjp.frq(CELEBS_00$air_fake_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Unfamiliar model")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real celeb (Ido Rosenblum)")

sjp.frq(CELEBS_00$waste_fake_person_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        xlim=c(0,110),
        axis.title="",
        title = "Unfamiliar model")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_ad_familiar,
        geom.size = 0.9,
        ylim=c(0,110),
        axis.title="",
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_positive_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_positive_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_positive_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_positive_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_negative_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,80),xlim=c(0.5,7.5),
        axis.title="",
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_negative_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,80),
        axis.title="",
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_negative_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,80),xlim=c(0.5,7.5),
        axis.title="",
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_negative_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,80),
        axis.title="",
        title = "Fake campaign")

>>>>

```{r , include=FALSE, echo=FALSE}
source("C:/SAAR/UNIVERSITY/R/SVIVA/code/experiment 2/SVIVA_exp2_dm_03.R")

SVIVA1_01 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/SVIVA1_01.csv")
CELEBS_00 = read.csv("C:/SAAR/UNIVERSITY/R/SVIVA/data/experiment 2 01-2018/CELEBS.csv")
```

```{r , include=FALSE, echo=FALSE}
library(tidyverse)
library(sjPlot)
library(stargazer)
library(ggthemes)

@@

```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
knitr::include_graphics("C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper2_JPART/revision/myfigures/fake_air_model.jpg")
```

@@

```{r, out.width = "400px", echo=FALSE,warning=FALSE,message=FALSE}
knitr::include_graphics("C:/SAAR/UNIVERSITY/R/SVIVA/papers/paper2_JPART/revision/myfigures/fake_waste_model.jpg")
```

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}

set_theme(
  base=theme_tufte(),
  geom.outline.size = 0.01,
  geom.outline.color = "white", 
  geom.label.size = 2,
  geom.label.color = "grey50")

sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_recognize,
        geom.size = 0.75,
        ylim=c(0,155),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real logo")

sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_recognize,
        geom.size = 0.75,
        ylim=c(0,155),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake logo")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(filter(SVIVA1_01,SYMBOL==2)$SVIVA_LOGO_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,160),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real logo")

sjp.frq(filter(SVIVA1_01,FAKE_LOGO_recognize!=0)$FAKE_LOGO_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,160),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
       title = "Fake logo")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_person_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real celeb (Tal Friedman)")

sjp.frq(CELEBS_00$air_fake_person_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Unfamiliar model")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_person_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real celeb (Ido Rosenblum)")

sjp.frq(CELEBS_00$waste_fake_person_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        xlim=c(0,110),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Unfamiliar model")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_ad_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_ad_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_ad_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_ad_familiar,
        geom.size = 0.75,
        ylim=c(0,110),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_positive_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_positive_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_positive_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_positive_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,40),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$air_real_negative_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,80),xlim=c(0.5,7.5),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (starting to think green)")

sjp.frq(CELEBS_00$air_fake_negative_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,80),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")

@@

```{r, echo=FALSE,warning=FALSE,message=FALSE, out.width=c('50%', '50%'),fig.show='hold', fig.width=5,fig.height=4}
sjp.frq(CELEBS_00$waste_real_negative_affect,
        type="hist",
        show.mean = T,
        ylim=c(0,80),xlim=c(0.5,7.5),
        axis.title="",
        geom.colors = alpha("springgreen3",0.8),
        title = "Real campaign (reusable bags)")

sjp.frq(CELEBS_00$waste_fake_negative_affect,
         type="hist",
        show.mean = T,
        ylim=c(0,80),
        axis.title="",
        geom.colors = alpha("dodgerblue4",0.8),
        title = "Fake campaign")
